---
title: "SI Parameters"
author: "Sascha Holzhauer"
date: "`r Sys.Date()`"
output: word_document
---


```{r, echo=FALSE, warnings=FALSE, message=FALSE, results='hide'}
source(simp$simpDefinition)
futile.logger::flog.threshold(futile.logger::ERROR, name='craftyr')
simp$sim$folder 	<- "_setA/_RegGlobMax"
setwd(paste(simp$dirs$simp, sep="/"))
source(paste(simp$dirs$simp, simp$sim$folder, "simp.R", sep="/"))

simp$sim$runids 	<- c(paste(preserve$run, "-0", sep=""))	# run to deal with
simp$sim$id			<- c(paste(preserve$run, "-0", sep=""))	# ID to identify specific data collections (e.g. regions)
simp$sim$task		<- c(paste(preserve$run, "-0", sep=""))	# Name of surrounding folder, usually a description of task 
simp$sim$endtick	<- 2040
```

## Agent Functional Types (AFT) Production
```{r, echo=FALSE, warnings=TRUE, message=TRUE, results='asis'}

for (aft in simp$mdata$aftNames[-1]) {
	data <- input_csv_param_productivities(simp, aft, filenameprefix = "AftProduction_",
				filenamepostfix = "_mono_medium")
	cat(paste("  \n###", aft, sep=""))
	print(knitr::kable(data,  format = "pandoc", 
		caption= paste("Capital sensitivities and productivities for AFT", aft)))	
}	
```

## Agent Functional Types (AFT) Parameters
```{r, echo=FALSE, warnings=TRUE, message=TRUE, results='asis'}
data <- hl_printAgentParameters(simp, filenameprefix  = "AftParams_",
		filenamepostfix = "", returnDataFrame = TRUE)
colnames(data)[colnames(data)=="serviceLevelNoiseMax"] <- "Noise"
knitr::kable(data, format = "pandoc", 
		caption= "AFT parameters. GU is Giving up, GI is giving in.")
```

## Benefit Functions
```{r, echo=FALSE, warnings=TRUE, message=TRUE, results='asis'}
functions <- hl_getCompetitionFunctions(simp, returntext = TRUE)
knitr::kable(data.frame(Service = names(functions), Function = functions), row.names = FALSE)
```

## Service Demands
```{r, echo=FALSE, warnings=TRUE, message=TRUE, results='asis'}

 knitr::kable(hl_table_demand(simp, dataname = "csv_aggregateServiceDemand", latex = FALSE, 
	forceparam = TRUE, regionset="13"), format = "pandoc",
caption="Demands for Services per year in region 13. Values for 2010 are chosen to approach the supply of initial land use,
		and trends resemble those of IPCC scenario B1.")
		
knitr::kable(hl_table_demand(simp, dataname = "csv_aggregateServiceDemand", latex = FALSE, 
	forceparam = TRUE, regionset="14"), format = "pandoc",
caption="Demands for Services per year in region 14. Values for 2010 are chosen to approach the supply of initial land use,
		and trends resemble those of IPCC scenario B1.")
		
knitr::kable(hl_table_demand(simp, dataname = "csv_aggregateServiceDemand", latex = FALSE, 
	forceparam = TRUE, regionset="27"), format = "pandoc",
caption="Demands for Services per year in region 27. Values for 2010 are chosen to approach the supply of initial land use,
		and trends resemble those of IPCC scenario B1.")